Percolation Analysis – Building a Package

### 2019-07-31 paper.Rmd
work on mapping - function.

## run analysis and save results of every run.

### input in source _file.txt

#source_file,map_name,shape_file_name,DTM_file_name
#BefundesBZ-minimal.csv, late bronze age features,alle_Schnitt-Fundstellen.shp,

### input in radius_values.txt (stays)

#upper_radius,lower_radius,step_value,limit,upper_threshold,lower_threshold,radius_unit
#500,2,1, 1000,0,0,1

@@

#source("R/mapping_clusters.v4.12.R")
#mapClusters()

>>>>

sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp"

@@

percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1)

source("R/mapping_clusters.v4.12.R")
mapClusters(data = data, shape = sNL_shape)
